Reassessing the Impact of Dynamic Slicing in SFL

### 2018-11-12 paper/main.tex
pass on Section 3

%% In general, updates in the matrix results in an increase of
%% suspiciousness for a given component when the target test is passing
%% or a reduction of suspiciousness when the target test is failing.

@@

For those statements $j$ which are not part of the slice of a failing
test, the combination reduces the value of $\N{11}$ and increases the
value of $\N{01}$. Therefore, suspiciosness of those statements
decrease. In this example, components $c_3$ and $c_4$, which are not
in the slice of $t_2$, have their suspiciousness reduced, enabling the
faulty component $c_2$ to rise from the third to the first position in
the ranking. \Mar{what about other formula?}

\Mar{think of another theorem...}

\subsection{Implementation}

@@

>>>>

\begin{theorem}
  The faulty statement may not be included in the critical slice of
  failing test cases.
\end{theorem}

It is possible that a slice that discards the faulty statement still
produces the expected message checked by the oracle. This can happen,
for example, if the oracle is too general.\qed

\Mar{Sofia, please add a short (3-4 lines at most) example based on
  one of our subjects} Section~\ref{sec:impl} explains the heuristics
we used to infer oracles for critical slicing that mitigates this
issue and Section~\ref{sec:eval} shows how often critical slicing
misses faulty statements.

@@

Considering the Ochiai formula, for those statements $j$ which are not
part of the slice of a failing test, the combination reduces the value
of $\N{11}$ and increases the value of $\N{01}$. Therefore,
suspiciosness of those statements decrease. Similar argument applies
to other fault predictors.\qed{}

In the example from Figure~\ref{fig:illustration}, components $c_3$
and $c_4$, which are not in the slice of $t_2$, have their
suspiciousness reduced, enabling the faulty component $c_2$ to rise
from the third to the first position in the ranking.

\subsection{Implementation}
\label{sec:impl}

@@

\Mar{...explain how we built our oracles/checkers...}
